Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-09-30 manuscript/Chapter3-manuscript.Rmd
update methods ms. add notes after talk with PO

We were provided raw data by the videogame company that spanned a period of 6 months of gameplay recorded for every player. The first recorded match was played on `r toString(format(min(dat$date)))`, and the last one on `r toString(format(max(dat$date)))`. We applied cleaning and filtering procedures on the raw data to produce a synthetic dataset for our analyses. The data that we analyzed were for matches where players did not know each other. We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero. Moreover, we used our knowledge of the game to delete any matches where players were potentially hacking, or not playing the game has it is supposed to be played. These matches were not considered as player experience.

@@

The behaviors that we analyzed were the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance per second traveled during a match (m/s).

>>>>

We were provided raw data by the videogame company that spanned a period of 6 months of gameplay recorded for every player. The first recorded match was played on `r toString(format(min(dat$date)))`, and the last one on `r toString(format(max(dat$date)))`. We applied cleaning and filtering procedures on the raw data to produce a synthetic dataset for our analyses. The data that we analyzed was for matches where players did not know each other. We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero. Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game has it is supposed to be played. These matches were not considered as player experience.

@@

The behaviors we analyzed were the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`). For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`).
